Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-16 main.tex
Updates from Overleaf

\author[0000-0003-1385-7591]{Song Huang (黄崧)}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Department of Astronomy and Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China}

\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-8873-5065]{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA \footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies analogous to the Milky Way. NSA is a catalog of parameters of local galaxies derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the new version of NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions. In this paper, we use the stellar mass derived from the ellpitical Petrosian photometry using \code{kcorrect v4\_2}. The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.

\section{LSBG search in HSC S18A}
Given an overview of the steps here.

@@

@@

\subsection{Radial distribution}\label{sec:radial_distr}
Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers). In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment. \citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile. In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.

@@

According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep{Bullock2001,Duffy2008,Dutton2014}. Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host. However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration $c\sim 8-10$. \citep{Gao2008,Dutton2014}. Comparing with this, the best-fit Einasto profiles for UDG (UPG) radial distribution have larger shape parameter $\alpha$ and smaller concentration $c$. We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis. Therefore, the UDG (UPG) radial distribution can be considered consistent with the dark matter distribution of the host. Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.

\subsection{Quenched fraction}\label{sec:quench}
Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched. Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.

UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields, however there are one or two red UDGs in fields. It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up? 3) how are they quenched? what's the correlation between quenching and puffing.

@@

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_dist2host}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac_host_color}
\end{figure*}

@@

\section{Discussion and Conclusion}
TODO: make data products (catalogs, fake UDGs, website for their images, etc.)

>>>>

\author[0000-0003-1385-7591]{Song Huang (黄崧)}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\affiliation{Department of Astronomy and Tsinghua Center for Astrophysics, Tsinghua University, Beijing 100084, China}
\author[0000-0002-8873-5065]{Peter Melchior}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2704-5028]{Remy Joseph}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Rachael Beaton}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-2991-9251]{Kirsten Casey}
\affiliation{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, Columbus, OH 43210, USA}
\author[0000-0002-1841-2252]{Shany Danieli}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Andy Goulding}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}
\author[0000-0002-1841-2252]{Erin Kado-Fong}
\affiliation{Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

@@

\subsection{NASA-Sloan Atlas}
We use the NASA-Sloan Atlas (NSA \footnote{\url{http://nsatlas.org}}, \citealt{Blanton2005,Blanton2011}) to select galaxies analogous to the Milky Way. NSA is a catalog of parameters of local galaxies derived from the Sloan Digital Sky Survey \citep[SDSS,][]{York2000}. We use the new version of NSA catalog (\code{v1\_0\_1}\footnote{\url{https://www.sdss.org/dr13/manga/manga-target-selection/nsa/}}) which contains about $640,000$ galaxies out to $z < 0.15$. It also includes elliptical Petrosian aperture photometry for galaxies, which is considered to be more reliable than the photometry used in older versions. In this paper, we use the stellar mass derived from the elliptical Petrosian photometry using \code{kcorrect v4\_2}. The redshifts of galaxies in NSA come from several spectroscopic surveys, gas surveys, or direct distance measurements.

\section{LSBG search in HSC S18A}
Given an overview of the steps here. Also read SMUDGES paper and discuss some aspects here.

@@

Our code \href{https://github.com/AstroJacobLi/kuaizi}{\code{kuaizi}} is also available on GitHub.

@@

\subsection{Radial distribution}\label{sec:radial_distr}

Since the discovery of UDGs in Coma cluster, the radial distribution of UDGs around the hosts has been a valuable tool to test various UDG formation theories (cite simulation papers). In \citet{vanDokkum2015}, UDGs are not found within 300 kpc from the cluster center, hinting that UDGs might not survive in such a dense environment. \citet{vdBurg2016} has also found that the number of UDGs is suppressed near the center of clusters, and the radial distribution of UDGs in cluster environments roughly follows a projected Einasto \citep{Einasto1965} profile. In the following, we derive the radial distribution of UDGs and UPGs in our sample and discuss possible implications.

@@

According to the concentration-mass relation of dark matter halos, the concentration of MW-like halo is $c_{\rm NFW} \sim 10$ \citep{Bullock2001,Duffy2008,Dutton2014}. Therefore, if assuming an NFW profile, the UDGs and UPGs follow the underlying dark matter distribution of the host. However, the Einasto shape parameter for a MW-like halo is $\alpha\sim 0.15$ at $z=0$ and its concentration $c\sim 8-10$. \citep{Gao2008,Dutton2014}. Comparing with this, the best-fit Einasto profiles for UDG (UPG) radial distribution have larger shape parameter $\alpha$ and smaller concentration $c$. We notice that the errors of the best-fit parameters are large due to the sample size and also the fact that concentration is most sensitive to data at smaller radial distances which are excluded in the analysis. Therefore, the UDG (UPG) radial distribution is considered to be consistent with the dark matter distribution of the host at a $2\sigma$ level. Nevertheless, a larger and more complete sample is needed to better constrain the radial distributions.

\subsection{Quenched fraction}\label{sec:quench}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{quenched_frac_dist2host.pdf}
		\includegraphics[width=1\linewidth]{quenched_frac_host_color.pdf}
	}
    \caption{Caption}
    \label{fig:qfrac}
\end{figure*}

Dwarf galaxy: most of them are blue in field, and most satellites of MW and larger groups/clusters are quenched. Among others, tidal stripping and ram-pressure stripping are thought to quench the satellites.

In this section we show the quenched fraction of UDG/UPGs without discussing too much about the physical implication on both UDG population and the general quenching-mass-size relation.

UDG quenching: most studies found red UDGs in clusters, blue UDGs in fields \citep{Prole2019,Leisman2017}, however there are one or two red UDGs in fields. It is unclear 1) are UDGs born to be large and diffuse (Amorisco); 2) if not, how are they puffed up? 3) how are they quenched? what's the correlation between quenching and puffing.

Find literature for quenched fraction as a function of distance to host (Einasto 1974, Spekkens2014, Karunakaran2022 for MW and M31).

@@

\section{Discussion and Conclusion}
TODO: make data products (catalogs, fake UDGs, website for their images, etc.)
\subsection{High quenched fraction of UDGs is an artifact}

@@

\subsection{UDG formation}
Discuss how does quenching and pufffing interplay.

Galaxy conformity: mass-size independent of color, jenny's quenched fraction independent of morph.

Pre-puffed up or pre-quenched?

Amorisco with my size distribution?
